Inefficient Concessions and Mediation

### 2020-02-11 draft.tex
move thm 4 assumption out of proof, into text (EJPE ref. 1)

\begin{theorem}
		Assume the high types are not patient enough to separate without concessions and that concessions have material value that can be destroyed. There are parameters under which the optimal equilibrium is a separating equilibrium in which concessions are inefficient.
	\label{theorem:4}
\end{theorem}

\emph{Proof}: See appendix.

@@

The no-concessions separating equilibrium also will exist if equation (6) holds. In the case that both exist, the high types will prefer the concessions separating equilibrium if and only if
\be
pX_{TT}^h+(1-p)X_{FF}^h - g_h \geq p(\frac{T}{1- \delta_h}) +(1-p)({-D}+\frac{\delta_h(W-D)}{1- \delta_h} )
\ee
This is simplified to preferring the concessions separating equilibrium if and only if
\be
 (1-p)W-p(T+D)\geq 0
\ee
i.e.,
\be
 W\geq p(W + T+D)
\ee
\\
\emph{Proof of Theorem \ref{theorem:4}:}\\
Because it is relatively complicated to calculate equilibrium concessions in the general case, we make a slight simplification of the general model here. Restrict functional forms of $T(\cdot),W(\cdot)$ and $D(\cdot)$ so that each is a scalar multiplied by its arguments. Also assume that $s_1=s_2=m_1=m_2=1.$ Because of linearity, equilibrium optimization has high types choosing $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choosing $\alpha=0$. Note that none of these simplifications is essential for the results to hold but we make them for ease of calculation and demonstration of the results. The low type's IC constraint binds so with $e=1$, the optimal concession can be calculated to be $g^1= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$. The high type's utility when $e=1$ is $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - g^1$.

>>>>

Before turning to our main result for the case where the material value of concessions can be destroyed, we make a slight simplification of the general model here. This is not essential for the results to hold; we make these simplifciations for ease of calculation and demonstration of the results. First, we restrict the functional forms of $T(\cdot),W(\cdot)$ and $D(\cdot)$ so that each is a scalar multiplied by its arguments. This linear functional form implies that equilibrium optimization has high types choosing $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choosing $\alpha=0$. To further simplify calculations, we also assume that $s_1=s_2=m_1=m_2=1.$

\begin{theorem}
		Assume the high types are not patient enough to separate without concessions and that concessions have material value that can be destroyed. There are parameters under which the optimal equilibrium is a separating equilibrium in which concessions are inefficient.
	\label{theorem:4}
\end{theorem}
\emph{Proof}: See appendix.

@@

The no-concessions separating equilibrium also will exist if equation (6) holds. In the case that both exist, the high types will prefer the concessions separating equilibrium if and only if
\be
pX_{TT}^h+(1-p)X_{FF}^h - g_h \geq p(\frac{T}{1- \delta_h}) +(1-p)({-D}+\frac{\delta_h(W-D)}{1- \delta_h} )
\ee
This is simplified to preferring the concessions separating equilibrium if and only if
\be
 (1-p)W-p(T+D)\geq 0
\ee
i.e.,
\be
 W\geq p(W + T+D)
\ee
\\
\emph{Proof of Theorem \ref{theorem:4}:}\\
Given the functional form restrictions that $T(\cdot),W(\cdot)$ and $D(\cdot)$ are each a scalar multiplied by its arguments and $s_1=s_2=m_1=m_2=1$, high types choose $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choose $\alpha=0$. Because the low type's IC constraint binds, with $e=1$ the optimal concession can be calculated to be $g^1= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$. The high type's utility when $e=1$ is then $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - g^1$.
